---
title: "Final_project"
author: "Kenneth Cruz"
format: html
echo: false
warning: false
---

```{r}
#| output: false
library(gtsummary)
library(tidyverse)
library(readxl)
library(here)
library(janitor)
here::here()
getwd()
final_project<-read_excel(here::here("R","final-project.xlsx"))

final_projectc<-clean_names(final_project)

final_projectx <-  final_projectc %>% 
	filter(health_workers_killed != 0)
```
```{r}
#| label: tbl-one
#| tbl-cap: "Descriptive Statistics of Incident Data in Palestine"
table_one<- tbl_summary(
	final_projectx,
	by=reported_perpetrator_name,
	include=c(number_of_attacks_on_health_facilities_reporting_damaged,health_workers_killed,health_workers_injured, health_transportation_destroyed),
	label=list(
		number_of_attacks_on_health_facilities_reporting_damaged ~ "Health Facilities Damaged",
		health_workers_killed ~ "Health Workers Killed",
		health_workers_injured ~ "Health Workers Injured",
		health_transportation_destroyed ~ "Health Transportation Destroyed"))

table_one
```
The number of health facilities damaged by the IDF is `r inline_text(table_one,variable="number_of_attacks_on_health_facilities_reporting_damaged", column = "stat_1")`
```{r}
total_hw_killed <-sum(final_projectx$health_workers_killed)
```

@tbl-one Shows the total number of health workers killed as of August 2024 in Palestine was `r total_hw_killed` workers.

```{r}
poisson_model <- glm(health_workers_killed ~ reported_perpetrator_name + 
										 	number_of_attacks_on_health_facilities_reporting_damaged + health_transportation_destroyed,
										 data = final_projectx, family = poisson)
```
```{r}
#| label: tbl-two
#| tbl-cap: "Regression Summary of Health Workers Killed vs. Perpetrator, Health Facilities Damaged and Health Transportation Destroyed"
tbl_regression(
	poisson_model,
	exponentiate=TRUE)
```
```{r}
daily_count<-function (n) {
	countee<-n
	return(table(final_project$`Health Workers Killed`== n))
}
daily_count(2)
daily_count(3)
```


```{r}
pdf(file = here::here("R", "histogram1.pdf"))

#| label: fig-hist
#| fig-cap: "Number of Health Workers Killed Daily"
histo1<-hist(final_projectx$health_workers_killed, 
     main = "Histogram of Health Workers Killed", 
     xlab = "Number Health Workers Killed Daily", 
     ylab = "Number of Observations", 
     col = "pink")
dev.off()
```
```{r}
#| label: fig-hist
#| fig-cap: "Number of Health Workers Killed Daily"
histo1<-hist(final_projectx$health_workers_killed, 
     main = "Histogram of Health Workers Killed", 
     xlab = "Number Health Workers Killed Daily", 
     ylab = "Number of Observations", 
     col = "pink")
```
@fig-hist Shows the number of health workers killed daily, and the number of observations for each incident.
